---
title: "ICD Table Analysis"
author: "Cindy Kartman"
date: "March 5, 2017"
output: word_document
---

```{r}
#############DIAGNOSIS ICD Table#############

library(readr)


diagnosis_icd<-read_delim("Z:/RawData/TextFormat/Diagnosis_ICD.txt", "|", escape_double = FALSE, trim_ws = TRUE)

str(diagnosis_icd)#8,536,894 obs. of  7 variables
head(diagnosis_icd)

#exploring number of unique values, what the unique values are, # of rows with values it and the # of rows with NA's
length(unique(diagnosis_icd$dx_rank))
table(diagnosis_icd$dx_rank)
sum(!is.na(diagnosis_icd$dx_rank))
sum(is.na(diagnosis_icd$dx_rank))


#Match "070" to icd dx column - 070 is prefix for Viral hepatitis so it includes all types of Hep C and it picks up other unrelated icd codes with "070" within
hep_c_icd_dx_v1 <- diagnosis_icd[grep("070", diagnosis_icd$icd_dx),] #grep search for matches to "070" within each element of a character vector:
dim(hep_c_icd_dx_v1)#30,153 rows
table(hep_c_icd_dx_v1$icd_dx)
table(hep_c_icd_dx_v1$icd_diagnosis)
length(unique(hep_c_icd_dx_v1$patient_id)) #4063 unique patient id's
```

```{r}
##Match icd 9 codes that have "Hepatitis C" in the description
hep_c_icd_dx_v2 <- subset(diagnosis_icd, 
                        icd_dx == "V02.62" | #Carrier or suspected carrier of Hep C (icd9)
                        icd_dx == "Z2252" | #Carrier or suspected carrier of Hep C (icd10)
                        icd_dx == "V12.09" | #Hepatitis C, history of (icd9)
                        icd_dx == "070.41" | #Acute hepatitis C with hepatic coma (icd9)
                        icd_dx == "070.44" | #Chronic hepatitis C with hepatic coma (icd9)
                        icd_dx == "070.51" | #Acute hepatitis C without mention of hepatic coma (icd9)
                        icd_dx == "070.54" | #Chronic hepatitis C without mention of hepatic coma; reat that it can be used as hep c in remission (icd9)
                        icd_dx == "070.7" | #Unspecified viral hepatitis C (icd9)
                        icd_dx == "070.70" | #Unspecified viral hepatitis C without hepatic coma (icd9)
                        icd_dx == "070.71" | #Unspecified viral hepatitis C with hepatic coma (icd9)
                        icd_dx == "B182"  | #Chronic viral hepatitis C (icd10)
                        icd_dx == "B1920" | #Unspecified viral hepatitis C without hepatic coma (icd10)
                        icd_dx == "B1710" | #Acute hepatitis C without hepatic coma (icd10)
                        icd_dx == "B1921" #Unspecified viral hepatitis C with hepatic coma (icd10)
                          )

#Codes below were not included - These are icd 10 codes - there doesn't seem to be specific Hep C codes during pregnancy for icd 9
#"O98411" (icd10) - Viral hepatitis complicating pregnancy, first trimester
#"O98412" (icd10) - Viral hepatitis complicating pregnancy, second trimester
#"O9842" (icd10) - "VIRAL HEPATITIS COMPLICATING CHILDBIRTH"  
#"O98413" (icd10) - "VIRAL HEPATITIS COMP PREGNANCY THIRD TRIMESTER" 

dim(hep_c_icd_dx_v2)#28,199 rows
table(hep_c_icd_dx_v2$icd_dx)
table(hep_c_icd_dx_v2$icd_diagnosis)

#Barplot
hep_c_icd_dx_v2_graph <- barplot(table(hep_c_icd_dx_v2$icd_dx), 
                                 xlab = "ICD Code", ylab = "Frequency", main = "# of Times ICD Code Appears in ICD Table",
                                 ylim = c(0, 20000))
text(hep_c_icd_dx_v2_graph, table(hep_c_icd_dx_v2$icd_diagnosis), labels = table(hep_c_icd_dx_v2$icd_diagnosis), pos = 3)

length(unique(hep_c_icd_dx_v2$patient_id)) #3,787 unique patient id's

#order by patient_id and then by encounter date
sorted_hep_c_icd_dx_v2 <- hep_c_icd_dx_v2[with(hep_c_icd_dx_v2, order(patient_id, enc_dt_ds)),]

#number of encounters per patient
num_of_encounters_per_patient <- as.data.frame(aggregate(encounter_id~patient_id, data = hep_c_icd_dx_v2, FUN = length))
colnames(num_of_encounters_per_patient) <- c("patient_id", "total_num_of_encounters")
num_of_encounters_per_patient[order(-num_of_encounters_per_patient$total_num_of_encounters),]#sort with most encounters on top


#find earilest hep C icd code using aggregate 
hep_c_patients_first_encounter_date <- aggregate(enc_dt_ds~patient_id,  data = hep_c_icd_dx_v2, min)

#merge with original dataset = to get each unique patients first encounter info
hep_c_patients_first_encounter_date <- merge(hep_c_patients_first_encounter_date, hep_c_icd_dx_v2)
####????????????format of date is changed??  Dates are showing up as date and time and date seems to be shifted by one day as if it was rounding up before??????????
hep_c_patients_first_encounter_date[order(hep_c_patients_first_encounter_date$patient_id),]

sum(hep_c_patients_first_encounter_date$first_encounter_date > "2014-01-01")#1558 patients whose first hep c encounter was after 01-01-2014
sum(hep_c_patients_first_encounter_date$first_encounter_date > "2015-01-01")#924 patients whose first hep c encounter was after 01-01-2015


#Create vector with id numbers of patients with a Hep C icd code
unique_hep_c_ids <- as.data.frame(unique(hep_c_icd_dx_v2$patient_id))
colnames(unique_hep_c_ids) <- "PATIENT_ID"
nrow(unique_hep_c_ids) #3787
write.csv(unique_hep_c_ids, "Z:/Hepatitis C Project/unique_hep_c_patient_ids.csv")
```

```{r}
#Match "Hepatitis" to icd description
hep_c_icd_diagnosis_v1 <- diagnosis_icd[grep("HEPATITIS", diagnosis_icd$icd_diagnosis),]#grep search for matches to "Hepatitis within each element of a character vector:
dim(hep_c_icd_diagnosis_v1)#39432 rows
table(hep_c_icd_diagnosis_v1$icd_diagnosis)
length(table(hep_c_icd_diagnosis_v1$icd_diagnosis))

#Barplot
hep_c_icd_diagnosis_v1_graph <- barplot(table(hep_c_icd_diagnosis_v1$icd_dx), 
                                 xlab = "ICD Code", ylab = "Frequency", main = "# of Times ICD Code Appears in ICD Table", cex.names = .5, 
                                 ylim = c(0, 20000))
#text(hep_c_icd_diagnosis_v1_graph, table(hep_c_icd_diagnosis_v1$icd_dx), labels = table(hep_c_icd_diagnosis_v1$icd_dx), cex = .5, pos = 3)

length(unique(hep_c_icd_diagnosis_v1$patient_id)) #6892 unique patient id's
```

```{r}
##Match icd 9 codes that have "Hepatitis C" in the description
hep_c_icd_diagnosis_v2 <- diagnosis_icd[grep("HEPATITIS C", diagnosis_icd$icd_diagnosis),]  #grep search for matches to "Hepatitis C"" within each element of a character vector:
dim(hep_c_icd_diagnosis_v2)#27445 rows
table(hep_c_icd_diagnosis_v2$icd_diagnosis)
length(table(hep_c_icd_diagnosis_v2$icd_diagnosis))
length(unique(hep_c_icd_diagnosis_v2$patient_id))#3322 unique patient id's

unique(hep_c_icd_diagnosis_v2$icd_dx)
unique(hep_c_icd_diagnosis_v2$icd_diagnosis)
```


```{r}
##Combine all table for hep C patients only
hep_c_patient_encounters <- merge(encounters, unique_hep_c_ids, by.x = "Patient_ID", by.y = "PATIENT_ID", all.x = FALSE, all.y = TRUE)
dim(hep_c_patient_encounters)
#order by increasing patient ID and decreaseing encounter date
hep_c_patient_encounters <- hep_c_patient_encounters[order(hep_c_patient_encounters$Patient_ID, hep_c_patient_encounters$Enc_DT_DS),]

##Merge encounter data with diagnosis icd dataset
hep_c_patient_merge_1 <- merge(hep_c_patient_encounters, diagnosis_icd, by.x = "Patient_ID", by.y = "patient_id", all.x = TRUE, all.y = FALSE)
dim(hep_c_patient_merge_1)

##Merge encounter data with cpt dataset
hep_c_patient_merge_2 <- merge(hep_c_patient_merge_1, cpt, by.x = "Patient_ID", all.x = TRUE, all.y = FALSE)

##Merge encounter data with med at admission
hep_c_patient_merge_3 <- merge(hep_c_patient_merge_2, med_rec_adm, by.x = "Patient_ID",all.x = TRUE, all.y = FALSE)

##Merge encounter data with meds at discharge
hep_c_patient_merge_4 <- merge(hep_c_patient_merge_3, med_rec_dc, by.x = "Patient_ID", all.x = TRUE, all.y = FALSE)

##Merge encounter data with med during inpatient stay
hep_c_patient_merge_5 <- merge(hep_c_patient_merge_4, meds_inpt, by.x = "Patient_ID", all.x = TRUE, all.y = FALSE)

##Merge encounter data with med during outpatient visit
hep_c_patient_merge_6 <- merge(hep_c_patient_merge_5, meds_outpt, by.x = "Patient_ID", all.x = TRUE, all.y = FALSE)

##Merge encounter data with procedure icd codes
hep_c_patient_merge_7 <- merge(hep_c_patient_merge_6, procedure_icd, by.x = "Patient_ID", all.x = TRUE, all.y = FALSE)

##Merge encounter data with social data from that encounter
hep_c_patient_encounters_all <- merge(hep_c_patient_merge_7, social_hx, by = "Patient_ID", all.x = TRUE, all.y = FALSE)



```
```{r}
#rename encounter date and id column
names(hep_c_patients_first_encounter_date)[names(hep_c_patients_first_encounter_date) == "enc_dt_ds"] <- "first_encounter_date"

names(hep_c_patients_first_encounter_date)[names(hep_c_patients_first_encounter_date) == "encounter_id"] <- "first_encounter_id"

#Merge first encounter date with hep c patient data to add first hep c encounter date and id  
hep_c_patient_encounters_all <- merge(hep_c_patient_encounters, hep_c_patients_first_encounter_date [, c("patient_id", "first_encounter_date", "first_encounter_id")], by.x = "Patient_ID", by.y = "patient_id", all.x = TRUE, all.y = FALSE)

#creating new column to determine whether encounter is before or after first hep c encounter
hep_c_patient_encounters_all$before_after_first_encounter <- ifelse(hep_c_patient_encounters_all$Enc_DT_DS >= hep_c_patient_encounters_all$first_encounter_date, "after", "before")

#can filter on before and after
```

```{r}
################Demo data for Hep C patients only##############
demo_hep_c_patients <- subset(demo, PATIENT_ID %in% unique_hep_c_patient_ids$PATIENT_ID) #3785 rows

#remove duplicated rows
demo_hep_c_patients <- demo_hep_c_patients[!duplicated(demo_hep_c_patients),] #3785 rows

demo_hep_c_patients[order(demo_hep_c_patients$PATIENT_ID),]

#find hep c patients listed with demographic data more than once
demo_hep_c_patients[duplicated(demo_hep_c_patients$PATIENT_ID),]#0 ids

demo_freq <- as.data.frame(table(demo_hep_c_patients$PATIENT_ID))#3785 unique id's


demo_hep_c_patients <- merge(demo_hep_c_patients, education, by.x = "PATIENT_ID", by.y = "PATIENT_ID", all.x = TRUE, all.y = FALSE)

sum(is.na(demo_hep_c_patients$YEARS_EDUCATION))#2883 missing

table(demo_hep_c_patients$Race)
table(demo_hep_c_patients$Ethnicity)
table(demo_hep_c_patients$language)
table(demo_hep_c_patients$Marital_Status)
sum(!is.na(demo_hep_c_patients$DOD_DS))#408 have died
table(demo_hep_c_patients$YEARS_EDUCATION)
```

```{r}
##########Zip Codes of Hep C patients#############

hep_c_patients_zip_code <- hep_c_patient_encounters[c("Patient_ID", "Encounter_ID", "Pat_Enc_Csn_ID_DID", "Enc_DT_DS", "Zip_Code_DID")]
dim(hep_c_patients_zip_code)
hep_c_patients_zip_code_freq <- as.data.frame(table(hep_c_patients_zip_code$Patient_ID))
colnames(hep_c_patients_zip_code_freq) <- c("Patient_ID", "Count_Zip_Code")
hep_c_patients_zip_code_freq[order(-hep_c_patients_zip_code_freq$Count_Zip_Code),]

```




```{r}
######ENCOUNTERS TABLE######

####Explore data

str(encounters)
tail(encounters)
dim(encounters)

#Patient_ID
summary(encounters$Patient_ID_fac)
sum(is.na(encounters$Patient_ID))

#Encounter_ID
sum(is.na(encounters$Encounter_ID))

#Pat_Enc_Csn_ID_DID
sum(is.na(encounters$Pat_Enc_Csn_ID_DID))

#Zip_Code_DID
sum(is.na(encounters$Zip_Code_DID))

#ENC_AGE
sum(is.na(encounters$ENC_AGE))

#Enc_EIO
sum(is.na(encounters$Enc_EIO))

#Enc_Type_c
sum(is.na(encounters$Enc_Type_c))

#Encounter_Type
sum(is.na(encounters$Encounter_Type))

#Fin_Class_C
sum(is.na(encounters$Fin_Class_C))

#Fin_Class
sum(is.na(encounters$Fin_Class))

#PCP_Prov_ID
sum(is.na(encounters$PCP_Prov_ID))

#PCP_Resource
sum(is.na(encounters$PCP_Resource))

#PCP_Prov_Service_C
sum(is.na(encounters$PCP_Prov_Service_C))

#PCP_Prov_Service
sum(is.na(encounters$PCP_Prov_Service))

#Enc_DT_DS
sum(is.na(encounters$Enc_DT_DS))

#Appt_DTTM_DS
sum(is.na(encounters$Appt_DTTM_DS))

#Appt_Checkin_DTTM
sum(is.na(encounters$Appt_Checkin_DTTM))

#Appt_Status_C
sum(is.na(encounters$Appt_Status_C))

#Appt_Status
sum(is.na(encounters$Appt_Status))

#Appt_Cancel_DTTM_DS
sum(is.na(encounters$Appt_Cancel_DTTM_DS))

#Appt_Primary_Loc_ID
sum(is.na(encounters$Appt_Primary_Loc_ID))

#Appt_Primary_Location
sum(is.na(encounters$Appt_Primary_Location))

#Appt_Dept_ID
sum(is.na(encounters$Appt_Dept_ID))

#Appt_Dept
sum(is.na(encounters$Appt_Dept))

#Appt_Prov_ID
sum(is.na(encounters$Appt_Prov_ID))

#Appt_Resource
sum(is.na(encounters$Appt_Resource))

#Appt_Prov_Service_C
sum(is.na(encounters$Appt_Prov_Service_C))

#Appt_Prov_Service
sum(is.na(encounters$Appt_Prov_Service))

#ED_Arrival_DTTM_DS
sum(is.na(encounters$ED_Arrival_DTTM_DS))

#ED_Disposition_C
sum(is.na(encounters$ED_Disposition_C))

#ED_Disposition
sum(is.na(encounters$ED_Disposition))

#Hsp_Adm_DTTM_DS
sum(is.na(encounters$Hsp_Adm_DTTM_DS))

#Hsp_Disch_DTTM_DS
sum(is.na(encounters$Hsp_Disch_DTTM_DS))

#LOS_Days
sum(is.na(encounters$LOS_Days))

#LOS_Hrs
sum(is.na(encounters$LOS_Hrs))

#Means_of_Arrival_C
sum(is.na(encounters$Means_of_Arrival_C))

#Means_of_Arrival
sum(is.na(encounters$Means_of_Arrival))

#Admit_Source_C
sum(is.na(encounters$Admit_Source_C))

#Admit_Source
sum(is.na(encounters$Admit_Source))

#First_Enc_Dept
sum(is.na(encounters$First_Enc_Dept))

#First_Enc_Service
sum(is.na(encounters$First_Enc_Service))

#First_Prov_ID
sum(is.na(encounters$First_Prov_ID))

#First_Resource
sum(is.na(encounters$First_Resource))

#First_Prov_Specialty_C
sum(is.na(encounters$First_Prov_Specialty_C))

#First_Prov_Specialty
sum(is.na(encounters$First_Prov_Specialty))

#Center_C
sum(is.na(encounters$Center_C))

#Center
sum(is.na(encounters$Center))

#Room
sum(is.na(encounters$Room))

#Last_Enc_Dept
sum(is.na(encounters$Last_Enc_Dept))

#Last_Enc_Service
sum(is.na(encounters$Last_Enc_Service))

#Last_Prov_ID
sum(is.na(encounters$Last_Prov_ID))

#Last_Resource
sum(is.na(encounters$Last_Resource))

#Last_Prov_Specialty_C
sum(is.na(encounters$Last_Prov_Specialty_C))

#Last_Prov_Specialty
sum(is.na(encounters$Last_Prov_Specialty))

#Disch_Dispo_C
sum(is.na(encounters$Disch_Dispo_C))

#Disch_Dispo
sum(is.na(encounters$Disch_Dispo))

#Pt_Encs
sum(is.na(encounters$Pt_Encs))

#Service_Area_C
sum(is.na(encounters$Service_Area_C))

#Service_Area
sum(is.na(encounters$Service_Area))

```




```{r cars}
########CPT File##########

str(cpt)
head(cpt)
dim(cpt)

#Patient ID
length(unique(cpt$patient_id))
sum(is.na(cpt$patient_id))

#collection of venous blood by venipuncture
subset(cpt, CPT == "36415") #32340

#Hep C antibody screening, for individual at high risk and other covered indication
subset(cpt, CPT == "G0472") #0

#Hepatitis C Anitbody
subset(cpt, CPT == "86803") #318

#Hepatitis C, confirmatory test (with reflex)
subset(cpt, CPT == "86804") #2

#Hepatitis C, direct probe technique
subset(cpt, CPT == "87520") #0

#Hepatitis C, amplified probe
subset(cpt, CPT == "87521") #0

#Hepatitis C, quantification
subset(cpt, CPT == "87522") #256

#Hepatitis C virus(HCV) genotype test
subset(cpt, CPT == "87902") #20

#Hepatitis C, genotype test
subset(cpt, CPT == "3266F") #88

#Anti-Nuclear Antibodies(ANA)
subset(cpt, CPT == "86038") #0


```


```{r}
##########Med_Rec_Adm File########

str(med_rec_adm)
dim(med_rec_adm)
head(med_rec_adm)
names(med_rec_adm)

#Patient ID
length(unique(med_rec_adm$PATIENT_ID))
sum(is.na(med_rec_adm$PATIENT_ID))

#Encounter ID
length(unique(med_rec_adm$ENCOUNTER_ID))
sum(is.na(med_rec_adm$ENCOUNTER_ID)) 

#Serial # for ethe patient contact
length(unique(med_rec_adm$PAT_ENC_CSN_ID_DID))
sum(is.na(med_rec_adm$PAT_ENC_CSN_ID_DID)) 

#Billing type of encouter
table(med_rec_adm$Enc_EIO)
sum(is.na(med_rec_adm$Enc_EIO))

#Encounter category type - integar
table(med_rec_adm$ENC_TYPE_C) 
sum(is.na(med_rec_adm$ENC_TYPE_C))

#Encounter Type - descriptive
med_rec_adm$ENCOUNTER_TYPE
table(med_rec_adm$ENCOUNTER_TYPE) 
sum(is.na(med_rec_adm$ENCOUNTER_TYPE))

#Hospital admission date and time
med_rec_adm$Hsp_Adm_DTTM_DS
sum(is.na(med_rec_adm$Hsp_Adm_DTTM_DS))

#Hospital discharge date and time
med_rec_adm$Hsp_Disch_DTTM_DS
sum(is.na(med_rec_adm$Hsp_Disch_DTTM_DS))

#Code for location of medication reconciliation
med_rec_adm$ADMIT_DEPT_ID
dim(table(med_rec_adm$ADMIT_DEPT_ID))
sum(is.na(med_rec_adm$ADMIT_DEPT_ID))

#Location of med reconciliation - descricption
med_rec_adm$ADMIT_DEPT
table(med_rec_adm$ADMIT_DEPT) 
sum(is.na(med_rec_adm$ADMIT_DEPT))

#Code for service providering care for patient
med_rec_adm$ADMIT_SERV_C
table(med_rec_adm$ADMIT_SERV_C)
sum(is.na(med_rec_adm$ADMIT_SERV_C))

#Service providing care for patient - descirptive
med_rec_adm$ADMIT_SERVICE_AREA
dim(table(med_rec_adm$ADMIT_SERVICE_AREA))
sum(is.na(med_rec_adm$ADMIT_SERVICE_AREA))

#Code for medication confirmed with patient upon admission or discharge
med_rec_adm$MED_REC_EVENT_C
table(med_rec_adm$MED_REC_EVENT_C)
sum(is.na(med_rec_adm$MED_REC_EVENT_C))

#medication confirmed with patient upon admit or discharge - descriptive
med_rec_adm$MED_REC_EVENT
table(med_rec_adm$MED_REC_EVENT)
sum(is.na(med_rec_adm$MED_REC_EVENT))

#was patient inpatient or outpatient - all outpatient
med_rec_adm$MED_ORDERING_MODE
table(med_rec_adm$MED_ORDERING_MODE)
sum(is.na(med_rec_adm$MED_ORDERING_MODE))

#Date med was ordered
med_rec_adm$MED_ORDER_DTTM_DS
sum(is.na(med_rec_adm$MED_ORDER_DTTM_DS))

#date med was discontinued
med_rec_adm$MED_DC_DTTM_DS
sum(is.na(med_rec_adm$MED_DC_DTTM_DS))

#date med was reconciled
med_rec_adm$MED_REC_DTTM_DS
sum(is.na(med_rec_adm$MED_REC_DTTM_DS))

#All values are the same - 35000
med_rec_adm$MED_REC_TYPE_C
table(med_rec_adm$MED_REC_TYPE_C)
sum(is.na(med_rec_adm$MED_REC_TYPE_C))

#all values are the same - "IP Admission Reconciliation""
med_rec_adm$MED_REC_TYPE
table(med_rec_adm$MED_REC_TYPE)
sum(is.na(med_rec_adm$MED_REC_TYPE))

#Code for determined status of meds during reconciliation
med_rec_adm$MED_REC_ACTION_C
table(med_rec_adm$MED_REC_ACTION_C)
sum(is.na(med_rec_adm$MED_REC_ACTION_C))

#Determined status of meds during reconciliation - descriptive
med_rec_adm$MED_REC_ACTION
table(med_rec_adm$MED_REC_ACTION)
sum(is.na(med_rec_adm$MED_REC_ACTION))
   
# "RSN_FOR_DISCON_C"   "RSN_FOR_DISCON_MED"
med_rec_adm$RSN_FOR_DISCON_C
table(med_rec_adm$RSN_FOR_DISCON_C)
sum(is.na(med_rec_adm$RSN_FOR_DISCON_C))

med_rec_adm$RSN_FOR_DISCON_MED
table(med_rec_adm$RSN_FOR_DISCON_MED)
sum(is.na(med_rec_adm$RSN_FOR_DISCON_MED))

#[25] "MEDICATION_ID"      "MEDICATION"   

med_rec_adm$MEDICATION_ID
length(unique(med_rec_adm$MEDICATION_ID))
sum(is.na(med_rec_adm$MEDICATION_ID))

med_rec_adm$MEDICATION
length(unique(med_rec_adm$MEDICATION))
sum(is.na(med_rec_adm$MEDICATION))


med_rec_adm$ORDER_MED_DOSE
length(unique(med_rec_adm$ORDER_MED_DOSE))
sum(is.na(med_rec_adm$ORDER_MED_DOSE))

#how med was administered - IV, topical, oral
med_rec_adm$MED_ROUTE
table(med_rec_adm$MED_ROUTE)
sum(is.na(med_rec_adm$MED_ROUTE))

#How often the med needs to be taken
med_rec_adm$ORDER_MED_FREQ
dim(table(med_rec_adm$ORDER_MED_FREQ))
sum(is.na(med_rec_adm$ORDER_MED_FREQ))

#Code for Therapeutic status
med_rec_adm$THERA_CLASS_C
dim(table(med_rec_adm$THERA_CLASS_C))
sum(is.na(med_rec_adm$THERA_CLASS_C))

#Descriptive for Therapeutic status
med_rec_adm$THERA_CLASS
dim(table(med_rec_adm$THERA_CLASS))
sum(is.na(med_rec_adm$THERA_CLASS))

#Code for Pharmaceutical class
med_rec_adm$PHARM_CLASS_C
dim(table(med_rec_adm$PHARM_CLASS_C))
sum(is.na(med_rec_adm$PHARM_CLASS_C))

#Descriptive for Pharmaceutical class
med_rec_adm$PHARM_CLASS
dim(table(med_rec_adm$PHARM_CLASS))
sum(is.na(med_rec_adm$PHARM_CLASS))


#Code for pharmaceutical sub class name
med_rec_adm$PHARM_SUBCLASS_C
dim(table(med_rec_adm$PHARM_SUBCLASS_C))
sum(is.na(med_rec_adm$PHARM_SUBCLASS_C))

#Descriptive for pharmaceutical sub class name
med_rec_adm$PHARM_SUB_CLASS
dim(table(med_rec_adm$PHARM_SUB_CLASS))
sum(is.na(med_rec_adm$PHARM_SUB_CLASS))

med_rec_adm$EVENT_MED_REC_LINE
dim(table(med_rec_adm$EVENT_MED_REC_LINE))
sum(is.na(med_rec_adm$EVENT_MED_REC_LINE))


anti_viral_med_rec_adm <- subset(med_rec_adm, THERA_CLASS == "ANTIVIRALS")

dim(anti_viral_med_rec_adm)#1296



```


```{r}
##########Med_Rec_Dc File########


#### explore data
str(med_rec_dc)
head(med_rec_dc)
names(med_rec_dc)
dim(med_rec_dc)

#Patient ID's
length(unique(med_rec_dc$PATIENT_ID))
sum(is.na(med_rec_dc$PATIENT_ID))

#Encournter ID
length(unique(med_rec_dc$ENCOUNTER_ID))
sum(is.na(med_rec_dc$ENCOUNTER_ID)) 

# serial # of patient contact
length(unique(med_rec_dc$PAT_ENC_CSN_ID_DID))
sum(is.na(med_rec_dc$PAT_ENC_CSN_ID_DID)) 

#encounter Type
table(med_rec_dc$ENC_TYPE_C) 
sum(is.na(med_rec_dc$ENC_TYPE_C))

med_rec_dc$ENC_TYPE
table(med_rec_dc$ENC_TYPE) 
sum(is.na(med_rec_dc$ENC_TYPE))

#Encounter Type
table(med_rec_dc$Enc_eio)
sum(is.na(med_rec_dc$Enc_eio))


#hopital admission date and time for 
med_rec_dc$Hsp_Adm_DTTM_DS
sum(is.na(med_rec_dc$Hsp_Adm_DTTM_DS))

#hopital discharge date and time
med_rec_dc$Hsp_Disch_DTTM_DS
sum(is.na(med_rec_dc$Hsp_Disch_DTTM_DS))

#location of medication reconciliation
med_rec_dc$DC_DEPT_ID
dim(table(med_rec_dc$DC_DEPT_ID))
table(med_rec_dc$DC_DEPT_ID)
sum(is.na(med_rec_dc$DC_DEPT_ID))

#location of med reconciliation = descriptive
med_rec_dc$DC_DEPT
table(med_rec_dc$DC_DEPT) 
sum(is.na(med_rec_dc$DC_DEPT))

#service line providing care for patient
med_rec_dc$DC_SERV_C
table(med_rec_dc$DC_SERV_C)
sum(is.na(med_rec_dc$DC_SERV_C))

#service line providing care for patients - descriptive
med_rec_dc$DC_SERVICE_AREA
dim(table(med_rec_dc$DC_SERVICE_AREA))
table(med_rec_dc$DC_SERVICE_AREA)
sum(is.na(med_rec_dc$DC_SERVICE_AREA))

#medication confirmed upon discharge - all same value
med_rec_dc$ADT_DC_EVENT_C
table(med_rec_dc$ADT_DC_EVENT_C)
sum(is.na(med_rec_dc$ADT_DC_EVENT_C))

#medication confirmed upon discharge - all same value
med_rec_dc$ADT_DC_EVENT
table(med_rec_dc$ADT_DC_EVENT)
sum(is.na(med_rec_dc$ADT_DC_EVENT))

#
med_rec_dc$DC_DISP_C
table(med_rec_dc$DC_DISP_C)
sum(is.na(med_rec_dc$DC_DISP_C))

#Disposition
med_rec_dc$DC_DISPOSITION
table(med_rec_dc$DC_DISPOSITION)
sum(is.na(med_rec_dc$DC_DISPOSITION))

#Med confirmed with patient upon discharge
med_rec_dc$MED_REC_EVENT_C
table(med_rec_dc$MED_REC_EVENT_C)
sum(is.na(med_rec_dc$MED_REC_EVENT_C))

#medication confirmed with patient upon discharge - all same value
med_rec_dc$MED_REC_EVENT
table(med_rec_dc$MED_REC_EVENT)
sum(is.na(med_rec_dc$MED_REC_EVENT))

#where medication ordered
med_rec_dc$MED_ORDERING_MODE
table(med_rec_dc$MED_ORDERING_MODE)
sum(is.na(med_rec_dc$MED_ORDERING_MODE))


med_rec_dc$MED_ORDER_DTTM_DS
sum(is.na(med_rec_dc$MED_ORDER_DTTM_DS))

med_rec_dc$MED_DC_DTTM_DS
sum(is.na(med_rec_dc$MED_DC_DTTM_DS))

med_rec_dc$MED_REC_DTTM_DS
sum(is.na(med_rec_dc$MED_REC_DTTM_DS))


med_rec_dc$MED_REC_TYPE_C
table(med_rec_dc$MED_REC_TYPE_C)
sum(is.na(med_rec_dc$MED_REC_TYPE_C))

#all values are the same but 1 is blank = "IP Discharge Reconciltion"
med_rec_dc$MED_REC_TYPE
table(med_rec_dc$MED_REC_TYPE)
sum(is.na(med_rec_dc$MED_REC_TYPE))

#determined status of medication during reconciliation
med_rec_dc$MED_REC_ACTION_C
table(med_rec_dc$MED_REC_ACTION_C)
sum(is.na(med_rec_dc$MED_REC_ACTION_C))

#determined status of medication during reconciliation - desciptive
med_rec_dc$MED_REC_ACTION
table(med_rec_dc$MED_REC_ACTION)
sum(is.na(med_rec_dc$MED_REC_ACTION))
   
# "RSN_FOR_DISCON_C"   "RSN_FOR_DISCON_MED"
med_rec_dc$RSN_FOR_DISCON_C
table(med_rec_dc$RSN_FOR_DISCON_C)
sum(is.na(med_rec_dc$RSN_FOR_DISCON_C))

med_rec_dc$RSN_FOR_DISCON_MED
table(med_rec_dc$RSN_FOR_DISCON_MED)
sum(is.na(med_rec_dc$RSN_FOR_DISCON_MED))

#"MEDICATION_ID"        

med_rec_dc$MEDICATION_ID
table(med_rec_dc$MEDICATION_ID)
dim(table(med_rec_dc$MEDICATION_ID))
sum(is.na(med_rec_dc$MEDICATION_ID))


#"MEDICATION" 
med_rec_dc$MEDICATION
table(med_rec_dc$MEDICATION)
dim(table(med_rec_dc$MEDICATION))
sum(is.na(med_rec_dc$MEDICATION))


#dosage of meds
med_rec_dc$ORDER_MED_DOSE
length(unique(med_rec_dc$ORDER_MED_DOSE))
sum(is.na(med_rec_dc$ORDER_MED_DOSE))

#how the med was administered
med_rec_dc$MED_ROUTE
table(med_rec_dc$MED_ROUTE)
dim(table(med_rec_dc$MED_ROUTE))
sum(is.na(med_rec_dc$MED_ROUTE))


#frequency of dosage
med_rec_dc$ORDER_MED_FREQ
dim(table(med_rec_dc$ORDER_MED_FREQ))
sum(is.na(med_rec_dc$ORDER_MED_FREQ))


med_rec_dc$THERA_CLASS_C
dim(table(med_rec_dc$THERA_CLASS_C))
sum(is.na(med_rec_dc$THERA_CLASS_C))

med_rec_dc$PHARM_CLASS_C
dim(table(med_rec_dc$PHARM_CLASS_C))
sum(is.na(med_rec_dc$PHARM_CLASS_C))

med_rec_dc$MED_PHARM_CLASS
dim(table(med_rec_dc$MED_PHARM_CLASS))
sum(is.na(med_rec_dc$MED_PHARM_CLASS))

med_rec_dc$PHARM_SUBCLASS_C
dim(table(med_rec_dc$PHARM_SUBCLASS_C))
sum(is.na(med_rec_dc$PHARM_SUBCLASS_C))

med_rec_dc$PHARM_SUB_CLASS
dim(table(med_rec_dc$PHARM_SUB_CLASS))
sum(is.na(med_rec_dc$PHARM_SUB_CLASS))

med_rec_dc$EVENT_MED_REC_LINE
dim(table(med_rec_dc$EVENT_MED_REC_LINE))
sum(is.na(med_rec_dc$EVENT_MED_REC_LINE))

```



```{r}
##########Meds_Inpt File########

str(meds_inpt)
head(meds_inpt)
dim(meds_inpt)


#Patient_ID and extract to CSV
sum(is.na(meds_inpt$Patient_ID))
write.table(meds_inpt$Patient_ID, file = paste("C:/Users/laura.olson/",'meds_inpt_Patient_ID.csv',sep = '/'), row.names = F) #save all Patient IDs as CSV

#Encounter_ID
sum(is.na(meds_inpt$Encounter_ID))

#Pat_Enc_Csn_ID_DID
sum(is.na(meds_inpt$Pat_Enc_Csn_ID_DID))

#HSP_ADM_DTTM_DS
sum(is.na(meds_inpt$HSP_ADM_DTTM_DS))

#HSP_Disch_DTTM_DS
sum(is.na(meds_inpt$HSP_Disch_DTTM_DS))

#Med_Dept
sum(is.na(meds_inpt$Med_Dept))

#Order_DT_DS
sum(is.na(meds_inpt$Order_DT_DS))

#Thera_class_c
sum(is.na(meds_inpt$Thera_class_c))

#Thera_class
sum(is.na(meds_inpt$Thera_class))

#Pharm_class_c
sum(is.na(meds_inpt$Pharm_class_c))

#Pharm_class
sum(is.na(meds_inpt$Pharm_class))

#Pharm_subclass_c
sum(is.na(meds_inpt$Pharm_subclass_c))

#Pharm_subclass
sum(is.na(meds_inpt$Pharm_subclass))

#Medication_id
sum(is.na(meds_inpt$Medication_id))

#Medication_id
sum(is.na(meds_inpt$Medication))

#GPI
sum(is.na(meds_inpt$GPI))

#Generic_name
sum(is.na(meds_inpt$Generic_name))

#Order_Med_Dose
sum(is.na(meds_inpt$Order_Med_Dose))

#Med_Route
sum(is.na(meds_inpt$Med_Route))

#Order_Med_Freq
sum(is.na(meds_inpt$Order_Med_Freq))

#Order_Start_DTTM_DS
sum(is.na(meds_inpt$Order_Start_DTTM_DS))

#Order_End_DTTM_DS
sum(is.na(meds_inpt$Order_End_DTTM_DS))

#MAR_Dose
sum(is.na(meds_inpt$MAR_Dose))

#MAR_Gave_DTTM_DS
sum(is.na(meds_inpt$MED_Gave_DTTM_DS))

#MAR_Sched_DTTM_DS
sum(is.na(meds_inpt$MED_Sched_DTTM_DS))

#MAR_Action
sum(is.na(meds_inpt$MAR_Action))

#Ordering_Mode
sum(is.na(meds_inpt$Ordering_Mode))

#Check cleaned data
str(meds_inpt)


```


```{r}
##########Meds_Outpt File########

str(meds_outpt)
head(meds_outpt)
dim(meds_outpt)

#Patient_ID
sum(is.na(meds_outpt$Patient_ID))

#Encounter_ID
sum(is.na(meds_outpt$Encounter_ID))

#Pat_Enc_Csn_ID_DID
sum(is.na(meds_outpt$Pat_Enc_Csn_ID_DID))

#Pat_Enc_DT_DS
sum(is.na(meds_outpt$Enc_DT_DS))

#Med_Dept
sum(is.na(meds_outpt$Med_Dept))

#Order_DT_DS
sum(is.na(meds_outpt$Order_DT_DS))

#Thera_class_c
sum(is.na(meds_outpt$Thera_class_c))

#Thera_class
sum(is.na(meds_outpt$Thera_class))

#Pharm_class_c
sum(is.na(meds_outpt$Pharm_class_c))

#Pharm_class
sum(is.na(meds_outpt$Pharm_class))

#Pharm_subclass_c
sum(is.na(meds_outpt$Pharm_subclass_c))

#Pharm_subclass
sum(is.na(meds_outpt$Pharm_subclass))

#Medication_id
sum(is.na(meds_outpt$Medication_id))

#Medication_id
sum(is.na(meds_outpt$Medication))

#GPI
sum(is.na(meds_outpt$GPI))

#Generic_name
sum(is.na(meds_outpt$Generic_name))

#SIG
sum(is.na(meds_outpt$SIG))

#QUANTITY
sum(is.na(meds_outpt$QUANTITY))

#REFILLS
sum(is.na(meds_outpt$REFILLS))

#Order_Med_Dose
sum(is.na(meds_outpt$Order_Med_Dose))

#Med_Route
sum(is.na(meds_outpt$Med_Route))

#Order_Med_Freq
sum(is.na(meds_outpt$Order_Med_Freq))

#Order_Start_DTTM_DS
sum(is.na(meds_outpt$Order_Start_DTTM_DS))

#Order_End_DTTM_DS
sum(is.na(meds_outpt$Order_End_DTTM_DS))

#Ordering_Mode
sum(is.na(meds_outpt$Ordering_Mode))

```


```{r}
##########Procedure_ICD File########

str(procedure_icd)
head(procedure_icd)
dim(procedure_icd)

```


```{r}
##########Social_Hx File########
str(social_hx)
head(social_hx)
dim(social_hx)
names(social_hx)

social_hx$Patient_ID
sum(is.na(social_hx$Patient_ID))

social_hx$Encounter_ID
sum(is.na(social_hx$Encounter_ID))

social_hx$Pat_Enc_Csn_ID_DID
sum(is.na(social_hx$Pat_Enc_Csn_ID_DID))

social_hx$Enc_DT_DS
sum(is.na(social_hx$Enc_DT_DS))

social_hx$Hx_SOURCE_C
sum(is.na(social_hx$Hx_SOURCE_C))
table(social_hx$Hx_SOURCE_C)

social_hx$Hx_SOURCE
sum(is.na(social_hx$Hx_SOURCE))
table(social_hx$Hx_SOURCE)

#Tobacco Use Status
social_hx$TOBACCO_USER_C
sum(is.na(social_hx$TOBACCO_USER_C))
table(social_hx$TOBACCO_USER_C)

social_hx$TOBACCO_USER
sum(is.na(social_hx$TOBACCO_USER))
table(social_hx$TOBACCO_USER)

social_hx$SMOKING_TOB_USE_C
sum(is.na(social_hx$SMOKING_TOB_USE_C))
table(social_hx$SMOKING_TOB_USE_C)

social_hx$SMOKING_TOB_USE
sum(is.na(social_hx$SMOKING_TOB_USE))
table(social_hx$SMOKING_TOB_USE)

social_hx$TOBACCO_PAK_PER_DY
sum(is.na(social_hx$TOBACCO_PAK_PER_DY))
table(social_hx$TOBACCO_PAK_PER_DY)

social_hx$TOBACCO_USED_YEARS
sum(is.na(social_hx$TOBACCO_USED_YEARS))
table(social_hx$TOBACCO_USED_YEARS)

social_hx$TOBACCO_COMMENT
sum(is.na(social_hx$TOBACCO_COMMENT))

social_hx$SMOKING_START_DATE_DS
sum(is.na(social_hx$SMOKING_START_DATE_DS))

social_hx$SMOKING_QUIT_DATE_DS
sum(is.na(social_hx$SMOKING_QUIT_DATE_DS))
     
social_hx$CIGARETTES_YN
sum(is.na(social_hx$CIGARETTES_YN))
table(social_hx$CIGARETTES_YN)

social_hx$PIPES_YN
sum(is.na(social_hx$PIPES_YN))
table(social_hx$PIPES_YN)

social_hx$CIGARS_YN
sum(is.na(social_hx$CIGARS_YN))
table(social_hx$CIGARS_YN)

social_hx$SMOKELESS_TOB_USE_C
sum(is.na(social_hx$SMOKELESS_TOB_USE_C))
table(social_hx$SMOKELESS_TOB_USE_C)

social_hx$SMOKELESS_TOB_USE
sum(is.na(social_hx$SMOKELESS_TOB_USE))
table(social_hx$SMOKELESS_TOB_USE)

social_hx$SNUFF_YN
sum(is.na(social_hx$SNUFF_YN))
table(social_hx$SNUFF_YN)

social_hx$CHEW_YN
sum(is.na(social_hx$CHEW_YN))
table(social_hx$CHEW_YN)

social_hx$SMOKELESS_QUIT_DATE_DS
sum(is.na(social_hx$SMOKELESS_QUIT_DATE_DS))

#Alchol
social_hx$ALCOHOL_USE_C
sum(is.na(social_hx$ALCOHOL_USE_C))
table(social_hx$ALCOHOL_USE_C)

social_hx$ALCOHOL_USE
sum(is.na(social_hx$ALCOHOL_USE))
table(social_hx$ALCOHOL_USE)

social_hx$HX_DRINK_TYPES_C
sum(is.na(social_hx$HX_DRINK_TYPES_C))
table(social_hx$HX_DRINK_TYPES_C)

social_hx$HX_DRINK_TYPES
sum(is.na(social_hx$HX_DRINK_TYPES))
table(social_hx$HX_DRINK_TYPES)

social_hx$ALCOHOL_DRINKS_WK
sum(is.na(social_hx$ALCOHOL_DRINKS_WK))
table(social_hx$ALCOHOL_DRINKS_WK)

social_hx$ALCOHOL_OZ_PER_WK
sum(is.na(social_hx$ALCOHOL_OZ_PER_WK))
table(social_hx$ALCOHOL_OZ_PER_WK)

social_hx$ALCOHOL_COMMENT
sum(is.na(social_hx$ALCOHOL_COMMENT))
table(social_hx$ALCOHOL_COMMENT)

#Drug Use
social_hx$ILL_DRUG_USER_C
sum(is.na(social_hx$ILL_DRUG_USER_C))
table(social_hx$ILL_DRUG_USER_C)

social_hx$ILL_DRUG_USER
sum(is.na(social_hx$ILL_DRUG_USER))
table(social_hx$ILL_DRUG_USER)

social_hx$IV_DRUG_USER_YN
sum(is.na(social_hx$IV_DRUG_USER_YN))
table(social_hx$IV_DRUG_USER_YN)

social_hx$ILLICIT_DRUG_FREQ
sum(is.na(social_hx$ILLICIT_DRUG_FREQ))
table(social_hx$ILLICIT_DRUG_FREQ)

social_hx$ILLICIT_DRUG_CMT
sum(is.na(social_hx$ILLICIT_DRUG_CMT))

#Sexual Activity
social_hx$SEXUALLY_ACTIVE_C
sum(is.na(social_hx$SEXUALLY_ACTIVE_C))
table(social_hx$SEXUALLY_ACTIVE_C)

social_hx$SEXUALLY_ACTIVE
sum(is.na(social_hx$SEXUALLY_ACTIVE))
table(social_hx$SEXUALLY_ACTIVE)

social_hx$FEMALE_PARTNER_YN
sum(is.na(social_hx$FEMALE_PARTNER_YN))
table(social_hx$FEMALE_PARTNER_YN)

social_hx$MALE_PARTNER_YN
sum(is.na(social_hx$MALE_PARTNER_YN))
table(social_hx$MALE_PARTNER_YN)

#Birth Control
social_hx$CONDOM_YN
sum(is.na(social_hx$CONDOM_YN))
table(social_hx$CONDOM_YN)

social_hx$PILL_YN
sum(is.na(social_hx$PILL_YN))
table(social_hx$PILL_YN)

social_hx$DIAPHRAGM_YN
sum(is.na(social_hx$DIAPHRAGM_YN))
table(social_hx$DIAPHRAGM_YN)

social_hx$IUD_YN
sum(is.na(social_hx$IUD_YN))
table(social_hx$IUD_YN)

social_hx$SURGICAL_YN
sum(is.na(social_hx$SURGICAL_YN))
table(social_hx$SURGICAL_YN)

social_hx$SPERMICIDE_YN
sum(is.na(social_hx$SPERMICIDE_YN))
table(social_hx$SPERMICIDE_YN)

social_hx$IMPLANT_YN
sum(is.na(social_hx$IMPLANT_YN))
table(social_hx$IMPLANT_YN)

social_hx$RHYTHM_YN
sum(is.na(social_hx$RHYTHM_YN))
table(social_hx$RHYTHM_YN)

social_hx$INJECTION_YN
sum(is.na(social_hx$INJECTION_YN))
table(social_hx$INJECTION_YN)

social_hx$SPONGE_YN
sum(is.na(social_hx$SPONGE_YN))
table(social_hx$SPONGE_YN)

social_hx$INSERTS_YN
sum(is.na(social_hx$INSERTS_YN))
table(social_hx$INSERTS_YN)

social_hx$ABSTINENCE_YN
sum(is.na(social_hx$ABSTINENCE_YN))
table(social_hx$ABSTINENCE_YN)

social_hx$SEX_COMMENT
sum(is.na(social_hx$SEX_COMMENT))

social_hx$UNKNOWN_FAM_HX_YN
sum(is.na(social_hx$UNKNOWN_FAM_HX_YN))
table(social_hx$UNKNOWN_FAM_HX_YN)

#Employment History
social_hx$OCCUPATION_C
sum(is.na(social_hx$OCCUPATION_C))
table(social_hx$OCCUPATION_C)

social_hx$OCCUPATION
sum(is.na(social_hx$OCCUPATION))
table(social_hx$OCCUPATION)

social_hx$EMPY_STATUS_C
sum(is.na(social_hx$EMPY_STATUS_C))
table(social_hx$EMPY_STATUS_C)

social_hx$EMPLOYMENT_STATUS
sum(is.na(social_hx$EMPLOYMENT_STATUS))
table(social_hx$EMPLOYMENT_STATUS)


```


```{r}
###############Demo File##############
demo<-read_delim("Z:/RAW NEW 3.28.2017/Demo_no_ED_20170329.txt", "|", escape_double = FALSE, trim_ws = TRUE)#Cindy's data path for new demo table

str(demo)
dim(demo)

#patient id
demo$PATIENT_ID
sum(is.na(demo$PATIENT_ID))

#DOB
demo$DOB_DS
sum(is.na(demo$PATIENT_ID))

#Gender
demo$Gender
unique(demo$Gender)
(table(demo$Gender))
sum(is.na(demo$Gender))

#Flag Gender
demo$Flag_Gender
unique(demo$Flag_Gender)
sum(is.na(demo$Flag_Gender))

#Race
demo$Race_Code
unique(demo$Race_Code)
(table(demo$Race_Code))
sum(is.na(demo$Race_Code))

demo$Race
unique(demo$Race)
(table(demo$Race))
sum(is.na(demo$Race))

#Ethnic
demo$Ethnic_Code
unique(demo$Ethnic_Code)
(table(demo$Ethnic_Code))
sum(is.na(demo$Ethnic_Code))

demo$Ethnicity
unique(demo$Ethnicity)
(table(demo$Ethnicity))
sum(is.na(demo$Ethnicity))

#Language
demo$Language_Code
unique(demo$Language_Code)
(table(demo$Language_Code))
sum(is.na(demo$Language_Code))

demo$Language
unique(demo$Language)
dim(table(demo$Language))
sum(is.na(demo$Language))

#Marital_Status
demo$Marital_Status_Code
unique(demo$Marital_Status_Code)
dim(table(demo$Marital_Status_Code))
sum(is.na(demo$Marital_Status_Code))

demo$Marital_Status
unique(demo$Marital_Status)
(table(demo$Marital_Status))
sum(is.na(demo$Marital_Status))

#Date of Death
demo$DOD_DS
sum(is.na(demo$DOD_DS))


